MapReduce to My Ears\\ {\Large Using Big Data for Music Synthesis}

### 2013-05-10 writeup/paper.tex
removed code examples, fixed things amanda mentioned

Our system takes in ordered sets of images and produces a MIDI file.
In our view, a MIDI file consists of note and duration pairs.  Taken
together, these constitute a score by chaining together multiple pairs
over the course of time:

@@

\subsection{Conversion to intermediate representation}
\label{sec:conversion}

Image data comes in a variety of different formats: JPEG, GIF, PNG,
etc..  Dealing with the plethora of formats presents a problem for our
translation because there are many artifacts of the formats
(annotations, geotagging, compression, etc..) which are unnecessary
for our implementation.  To keep the core abstraction of images as
arrays of bytes (the abstraction described in
Section~\ref{sec:overview}) the first stage of our Hadoop
implementation\footnote{\code{src/main/phase1}} converts the surface
image representation to the sequence file format used in subsequent
processing.  Although it may appear inefficient to hold an
uncompressed image in memory, this is actually ideal for Hadoop:
because computing cycles (incurred through recompressing and sending
the images) are the cost, compared with network traffic.

@@

\begin{figure}
\begin{lstlisting}[language=Java]
public class WriteImgsToSequence
{
  BufferedImage img = null;
  SequenceFile.Writer writer=null;
  FileSystem fs = 
      FileSystem.get(conf);
  FileStatus[] fss = 
    fs.globStatus(new Path(input 
      + "/*.jpg"));
  writer = SequenceFile
      .createWriter(fs, 
    conf,outPath,IntWritable.class,
    ArrayListOfIntsWritable.class);
  int counter = 0;
  for (FileStatus status : fss) {
    IntWritable image_counter = 
      new IntWritable();
    ArrayListOfIntsWritable 
     pixelData = 
      new ArrayListOfIntsWritable();
    img = ImageIO.read(
      new File(status.getPath()
         .toString().substring(5)));
    // Get RBG for each pixel 
    for(int j = 0; j<thumbs; j++) {
     for(int i = 0; i<thumbs; i++) {
        pixelData
          .add(img.getRGB(i,j));
      }
    }
    // Write to the sequence file
    image_counter.set(counter);
    writer.append(image_counter,
      pixelData);
    counter += 1;
  } 
}
\end{lstlisting}
\caption{Snippet of code from \code{WriteToSequenceFile} showing
  format used in sequence files throughout the MapReduce jobs.}
\end{figure}

@@

After taking the image data to an intermediate format, we must map the
image data to a set of note / region pairs for use in the MIDI.  To do
this, we map a conversion function across each of the different
portions of each image.  The conversion happens by mapping over our
set of images in the \code{Image2MusicMR} class.  The output of the
image to music conversion is $n$ sets of note lists (where notes are
expressed as pairs).

@@

A snippet of our mapper is shown in
Figure~\ref{figure:colortomusic-mapper}.

\begin{figure}
\label{figure:colortomusic-mapper}
\begin{lstlisting}[language=Java]
public void map(IntWritable key, 
    ArrayListOfIntsWritable pixels,
    Context context)
{
  int regionCounter = 1;
  MidiNote midiNote = null;
  for(int i=0; i<pixels.size();i++){
    pixel = pixels.get(i);
    // Conversion from color to note
    midiNote = Color2Music
      .convert(new Color(pixel));
    REGION_IMAGENO.set(regionCounter,
      key.get());
    NOTE_VELOCITY.set(midiNote.getTone(),
      midiNote.getVelocity());
    context.write(REGION_IMAGENO,
       NOTE_VELOCITY);
    regionCounter++;
  }
}
\end{lstlisting}
\caption{A portion of our mapper that takes color data to MIDI notes.
  For each pixel in the original image, the conversion in
  \code{Color2Music} is applied before setting the output key (as a
  region, number pair).}
\end{figure}

>>>>

Our system takes in ordered sets of images and produces a MIDI file.
The input format is JPEG images: this is a very commonly used lossy
compression format.  Since we used input corpuses from the internet,
using JPEG worked for the variety of input formats.  Using JPEG as the
input format is also attractive because it can be easily unpacked by
the Java \code{ImageBuffer} class.

The output of our MapReduce phases is MIDI music.  MIDI is a simple
format for writing music which can be mixed ans synthesized using
software.  At an abstract level, a MIDI file consists of note and
duration pairs.  Taken together, these constitute a score by chaining
together multiple pairs over the course of time:

@@

\subsection{Conversion to intermediate representation}
\label{sec:conversion}
Image data comes in a variety of different formats: JPEG, GIF, PNG,
etc..  Dealing with the plethora of formats presents a problem for our
translation because there are many artifacts of the formats
(annotations, geotagging, compression, etc..) which are unnecessary
for our implementation.  To keep the core abstraction of images as
arrays of bytes (the abstraction described in
Section~\ref{sec:overview}) the first stage of our Hadoop
implementation converts the surface image representation to the
sequence file format used in subsequent processing.  Although it may
appear inefficient to hold an uncompressed image in memory, this is
actually ideal for Hadoop: because computing cycles (incurred through
recompressing and sending the images) are the cost, compared with
network traffic.

@@

@@

After taking the image data to an intermediate format, we must map the
image data to a set of note / region pairs for use in the MIDI.  To do
this, we map a conversion function across each of the different
portions of each image.  The conversion happens by mapping over our
set of images in the \code{Image2MusicMR} class.  The input of this
reducer is a set of key/value pairs which constitute the image number
and image data (a set of integers representing each pixel in the
image).  The output of the image to music conversion is $n$ sets of
note lists (where notes are expressed as pairs).  This is stored as a
set of key/value pairs where the key is the region number and image
number pair (subsequently discussed, but used for secondary sorting)
and the part number and MIDI note.

@@
